---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.path = "README-")
```

## Introduction to Data Visualisation and Web Applications Using R
### By: Osama Mahmoud, Luke A. McGuinness and Chris Penfold

[![Build Status](https://travis-ci.org/statcourses/BristolVis.svg?branch=master)](https://travis-ci.org/statcourses/BristolVis)

This page provides materials and practicals of the [data visualisation course](http://www.bristol.ac.uk/medical-school/study/short-courses/Introduction-to-Data-Visualisation-and-Web-Applications-Using-R/) held at the University of Bristol, November 2019.

## Installing the `BristolVis` package

The course uses a variety of data examples, R packages and practical sheets. The easiest way of downloading and installing all dependencies is to install the R package associated with this course, named 'BristolVis'. It can be simply installed by running the following code lines into your R session.

```{r eval=FALSE}
install.packages("drat")
drat::addRepo("statcourses")
install.packages("BristolVis")
```

## Course Materials:

  * **Introduction to R**: [Slides](https://raw.githubusercontent.com/statcourses/BristolVis/master/PDF_Slides/01_Intro_to_R.pdf) - [R script](https://raw.githubusercontent.com/statcourses/BristolVis/master/R_Scripts/Rscript_Intro-R.zip) - [Exercises](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/practical 1 - IntroR.pdf) - [Solutions](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/Answers 1 - IntroR.pdf).
  
  * **Base graphics**: [Slides](https://raw.githubusercontent.com/statcourses/BristolVis/master/PDF_Slides/03_Base_graphics.pdf) - [R script](https://raw.githubusercontent.com/statcourses/BristolVis/master/R_Scripts/Rscript_base-graphics.zip) - [Exercises](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/Practical 2 - Base graphics.pdf) - [Solutions](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/Answers 2 - Base graphics.pdf).
 
  * **Advanced graphics**: [Slides](https://raw.githubusercontent.com/statcourses/BristolVis/master/PDF_Slides/05_Advanced_graphics.pdf) - [R script](https://raw.githubusercontent.com/statcourses/BristolVis/master/R_Scripts/Rscript_advanced-graphics.zip) - [Exercises](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/Practical 3 - Advanced graphics.pdf) - [Solutions](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/Answers 3 - Advanced graphics.pdf).
  
  * **More on advanced graphics**: [Slides](https://raw.githubusercontent.com/statcourses/BristolVis/master/PDF_Slides/07_More_on_Advanced_graphics.pdf) - [R script](https://raw.githubusercontent.com/statcourses/BristolVis/master/R_Scripts/Rscript_more_on_advanced-graphics.zip) - [Exercises](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/Practical 4 - More on advanced graphics.pdf) - [Solutions](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/Answers 4 - More on advanced graphics.pdf).
  
  * **Interactive plots**: [Slides](https://raw.githubusercontent.com/statcourses/BristolVis/master/PDF_Slides/09_Interactive_plots.pdf) - [R script](https://raw.githubusercontent.com/statcourses/BristolVis/master/R_Scripts/Rscript_interactive_plots.zip) - [Exercises](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/Practical 5 - Interactive plots.pdf) - [Solutions](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/Answers 5 - Interactive plots.pdf).
  
  * **Inroduction to R Markdown**: [Slides](https://raw.githubusercontent.com/statcourses/BristolVis/master/PDF_Slides/11_Intro_RMarkdown.pdf) - [Exercises](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/RMarkdown/Practical 6 - RMarkdown.pdf) - Solutions are as follows:
    - Exercise 1: [Rmd file](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/RMarkdown/ans_RMarkdown_1.Rmd), [html output](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/RMarkdown/ans_RMarkdown_1.zip), [pdf output](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/RMarkdown/ans_RMarkdown_1.pdf), [word output](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/RMarkdown/ans_RMarkdown_1.docx).
    - Exercise 2: [Rmd file](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/RMarkdown/ans_RMarkdown_2.Rmd), [html output](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/RMarkdown/ans_RMarkdown_2.zip), [pdf output](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/RMarkdown/ans_RMarkdown_2.pdf), [word output](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/RMarkdown/ans_RMarkdown_2.docx).
    - Exercise 3: [Rmd file](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/RMarkdown/ans_RMarkdown_3.Rmd), [html output](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/RMarkdown/ans_RMarkdown_3.zip), [pdf output](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/RMarkdown/ans_RMarkdown_3.pdf), [word output](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/RMarkdown/ans_RMarkdown_3.docx).
    - Exercise 4: [Rmd file](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/RMarkdown/ans_RMarkdown_4.Rmd), [html output](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/RMarkdown/ans_RMarkdown_4.zip), [pdf output](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/RMarkdown/ans_RMarkdown_4.pdf), [word output](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/RMarkdown/ans_RMarkdown_4.docx).
    - Exercise 5: [Rmd file](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/RMarkdown/ans_RMarkdown_5.Rmd), [html output](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/RMarkdown/ans_RMarkdown_5.zip)
  
  * **Inroduction to Shiny**: [Slides](https://raw.githubusercontent.com/statcourses/BristolVis/master/PDF_Slides/13_Intro_shiny.pdf) - [Exercises 1](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/Shiny/practical 7_1_shiny.pdf) - [Exercises 2](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/Shiny/practical 7_2_shiny.pdf) - [Exercises 3](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/Shiny/practical 7_3_shiny.pdf) - [Exercises 4](https://raw.githubusercontent.com/statcourses/BristolVis/master/Practical_Exercises/Shiny/practical 7_4_shiny.pdf).
  
    
  * **Other useful materilas:**
    - The [R reference card](https://raw.githubusercontent.com/statcourses/BristolVis/master/Other_Materials/Refcard_IntroR.pdf) summarises basic concepts of R.
    - The R studio [cheat sheet for the ggplot2](https://raw.githubusercontent.com/statcourses/BristolVis/master/Other_Materials/ggplot2-cheatsheet.pdf) summarises functions of the `ggplot2` package.
    - The R studio [cheat sheet for web applications](https://raw.githubusercontent.com/statcourses/BristolVis/master/Other_Materials/shiny-cheatsheet.pdf) summarises functions of the `shiny` package.

## Usage of practicals via `BristolVis`

The practical exercises and their solutions can be displayed via the `BristolVis` package using:
```{r, eval=FALSE}
vignette("prac_IntroR", package = "BristolVis")
vignette("prac_base", package = "BristolVis")
vignette("prac_advanced", package = "BristolVis")
vignette("prac_AdvMore", package = "BristolVis")
vignette("prac_interactive", package = "BristolVis")
vignette("prac_RMarkdown", package = "BristolVis")
vignette("prac1_shiny", package = "BristolVis")
vignette("prac2_shiny", package = "BristolVis")
vignette("prac3_shiny", package = "BristolVis")
vignette("prac4_shiny", package = "BristolVis")
```

Solutions of some of these practical exercises can be displayed via the `BristolVis` package as follows:
```{r, eval=FALSE}
vignette("ans_IntroR", package = "BristolVis")
vignette("ans_base", package = "BristolVis")
vignette("ans_advanced", package = "BristolVis")
vignette("ans_AdvMore", package = "BristolVis")
vignette("ans_interactive", package = "BristolVis")
```

## Other resources

  * You can view the entire set of courses delivered by [Osama Mahmoud](http://www.bristol.ac.uk/expsych/people/osama-mahmoud/overview.html) and their associated R packages from [his personal website](http://osmahmoud.com/R-courses/) and the [stat-courses website](https://statcourses.github.io/).
    
  * You can view the github page created by [Chris Penfold](http://www.bristol.ac.uk/clinical-sciences/people/christopher-penfold/overview.html) for the R Markdown materials associated with this course [from here](https://github.com/Chris-M-P/Rmarkdown).
  
  * A shiny application developed by [Luke McGuinness](https://research-information.bristol.ac.uk/en/persons/luke-a-mcguinness(2c0401d0-499b-444b-b477-0631416ddf48).html) can be viewed [from here](https://mcguinlu.shinyapps.io/robvis/).
