---
title: "Answers - Interactive plots"
author: "Osama Mahmoud"
output: rmarkdown::html_vignette
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Practical - Interactive plots}
-->

Load the (*movies*) data set from the `BristolVis` R package. The data can be called and viewed using:

```{r, include=FALSE}
data(bmov, package = "BristolVis")
head(bmov)
```

### Scatter plots (15 minutes)

Let's start with some simple scatter plots using the `bmov` data:

1. Plot length Vs. rating using the advanced graphics package (ggplot2):
```{r, message=FALSE, warning=FALSE}
require(ggplot2)
require(plotly)
(G = ggplot(bmov, aes(Length, Rating)) + geom_point())
```

2. Use the `cut` function to generate a categorical form of the variable `Year` with sensible cutpoints.
```{r}
summary(bmov$Year)
bmov$cat_timing = cut(bmov$Year, breaks = c(1930, 1990, 2000, 2005))
```

3. Plot length Vs. rating such that points are coloured using categories of your generated timing:
```{r}
(G = ggplot(bmov, aes(Length, Rating, color = cat_timing)) + geom_point())
```

4. The default colors of the previous plot are terrible! use your own color selections to generate a better plot.

```{r}
(G = G + scale_color_manual(values = c("blue", "yellow", "red")))
```

5. Generate an interactive plot of the plot in (4) using the `plotly` package and name it `Fig_scatter`
```{r}
Fig_scatter = ggplotly(G)
```

6. Try to zoom in using your mouse by box selection to explore further detailed information


7. Save your interactive plot as an html file.
```{r, eval=FALSE}
htmlwidgets::saveWidget(Fig_scatter, "Fig_scatter.html")
```

### Histograms (10 minutes)
1. Use the `ggplot2` to plot a histogram of the movie years restricted to data after 1980.
```{r, message=FALSE, warning=FALSE}
(G = ggplot(bmov[bmov$Year>=1980,], aes(Year)) + geom_histogram())
```

2. Produce the same plot as in (1), but set the number of bins to 25.
```{r, message=FALSE, warning=FALSE}
(G = G + geom_histogram(bins = 25))
```

3. Generate an interactive plot of the plot in (2) using the `plotly` package and name it `Fig_hist`
```{r, message=FALSE, warning=FALSE}
Fig_hist = ggplotly(G)
```

4. Try to zoom in using your mouse by box selection to explore further detailed information and reset the plot (double-click)


5. Save your interactive plot as an html file.
```{r, eval=FALSE}
htmlwidgets::saveWidget(Fig_hist, "Fig_hist.html")
```


### Boxplots (10 minutes)
1. Generate a boxplot for the ratings data by generated categories of production timing using `ggplot2`.
```{r}
(G = ggplot(bmov, aes(x=cat_timing, y =Rating)) + geom_boxplot(aes(group = cat_timing)))
```


2. Try generating a similar interactive boxplot
```{r}
Fig_box = ggplotly(G)
```

3. save the interactive plot to an html file
```{r, eval=FALSE}
htmlwidgets::saveWidget(Fig_box, "Fig_box.html")
```


### Corrlation matrix (20 minutes)
1. Use the built-in `iris` data to compute a correlation matrix and correlation p-values for the continous (first four) variables
```{r}
data(iris)
head(iris)
require(ggcorrplot)
data_cont = iris[,1:4]
Corr = cor(data_cont)
corr.p = cor_pmat(data_cont)
```

2. Visualize the correlation matrix using the method = "circle"
```{r}
(G = ggcorrplot(Corr, method = "circle"))
```

3. Show the lower triangle using hierarchical clustering and `square` method rather than circle.
```{r}
(G = ggcorrplot(Corr, hc.order = TRUE, type = "lower"))
```

4. Use correlation significance level 0.01 to highlight the non-significant coefficient
```{r}
(G = ggcorrplot(Corr, hc.order = TRUE, type = "lower", p.mat = corr.p, sig.level = 0.01))
```

5. Use different shape - rather than the cross - to highlight the non-significant coefficient (use help of the function `ggcorrplot` by typing: `?ggcorrplot` to find out)
```{r}
(G = ggcorrplot(Corr, hc.order = TRUE, type = "lower", p.mat = corr.p, sig.level = 0.01, pch = 10))
```

6. Add coeficient values on the plot in (3)
```{r}
(G1 = ggcorrplot(Corr, hc.order = TRUE, type = "lower", lab = TRUE, lab_size = 3))
```

7.Produce interactive plot of the plot in (6)
```{r}
Fig_cor = ggplotly(G1)
```

7.save the interactive plot in as html.
```{r, eval=FALSE}
htmlwidgets::saveWidget(Fig_cor, "Fig_cor.html")
```
