---
title: "Answers 7 - Web applications"
author: "Osama Mahmoud"
output: rmarkdown::html_vignette
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Answers 7 - Web applications}
-->

### Create your own application (10 minutes)
Create a new directory named App-training in your working directory. Then copy and paste the ***app.R*** script (the script from myApp). 

Launch your app by running `runApp("App-training")`. Then close the app and make some changes to your script:

1. Change the title from *Pain medication data* to your own title.
2. Set the minimum value of the slider bar to 10.
3. Set the starting value of the slider bar to 20.
4. Change the histogram border color from "white" to "purple"

```{r solution, echo=TRUE, eval=FALSE}
library(shiny)

# Define UI for application that draws a histogram
ui <- fluidPage(
   
   # Application title
   titlePanel("My own title ..."),
   
   # Sidebar with a slider input for number of bins 
   sidebarLayout(
      sidebarPanel(
         sliderInput("bins",
                     "Number of bins:",
                     min = 10,
                     max = 50,
                     value = 20)
      ),
      
      # Show a plot of the generated distribution
      mainPanel(
         plotOutput("distPlot")
      )
   )
)

# Define server logic required to draw a histogram
server <- function(input, output) {
   output$distPlot <- renderPlot({
      # generate bins based on input$bins from ui.R
      data(med, package = "BristolVis")
      x    <- med$time 
      bins <- seq(min(x), max(x), length.out = input$bins + 1)
      
      # draw the histogram with the specified number of bins
      hist(x, breaks = bins, col = 'darkblue', border = 'purple',
           main = "Histogram of time to relief",
           xlab = "Time to relief (hours)")
   })
}

# Run the application 
shinyApp(ui = ui, server = server)
```

### View and edit Shiny examples (15 minutes)

You can copy and modify existing Shiny apps. Here is a list of app examples that you can copy their scripts and play with:

```{r, eval=FALSE}
runExample("01_hello")      # a histogram
runExample("02_text")       # tables and data frames
runExample("03_reactivity") # a reactive expression
runExample("04_mpg")        # global variables
runExample("05_sliders")    # slider bars
runExample("06_tabsets")    # tabbed panels
runExample("07_widgets")    # help text and submit buttons
runExample("08_html")       # Shiny app built from HTML
runExample("09_upload")     # file upload wizard
runExample("10_download")   # file download wizard
runExample("11_timer")      # an automated timer
```

### Add control widgets (30 minutes)

In your `App-training` modify your scripts to:
1. add radio buttons with three colors from which a user can choose to change the histogram color.

2. add a single check box when ticked the probability densities are plotted with the histogram rather than the frequencies.

```{r echo=TRUE, eval=FALSE}
library(shiny)

# Define UI for application that draws a histogram
ui <- fluidPage(

  # Application title
  titlePanel("Pain medication data"),

  # Sidebar with a slider input for number of bins
  sidebarLayout(
    sidebarPanel(
      sliderInput("bins",
                  "Number of bins:",
                  min = 1,
                  max = 50,
                  value = 30),

      hr(),

      radioButtons("col",
                  "Histogram color:",
                  choices = c('Red' = 'red', 'Orange' = 'orange', 'Dark green' = 'darkgreen'),
                  selected = 'red'),

      hr(),

      checkboxInput("prop", "Plot probabilities")
    ),

    # Show a plot of the generated distribution
    mainPanel(
      plotOutput("distPlot")
    )
  )
)

# Define server logic required to draw a histogram
server <- function(input, output) {
  output$distPlot <- renderPlot({
    # generate bins based on input$bins from ui.R
    data(med, package = "BristolVis")
    x    <- med$time
    bins <- seq(min(x), max(x), length.out = input$bins + 1)

    # draw the histogram with the specified number of bins
    hist(x, breaks = bins, col = input$col, border = 'white', probability = input$prop,
         main = "Histogram of time to relief",
         xlab = "Time to relief (hours)")
  })
}

# Run the application
shinyApp(ui = ui, server = server)
```

