---
title: "Answers 6 - Interactive documents"
author: "Osama Mahmoud"
output: rmarkdown::html_vignette
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Practical 1}
-->

## Interactive documents using R Markdown
Unlike the traditional workflow of creating static reports, you can create reports that allow your readers to change the assumptions underlying your analysis and see the results immediately. This can be done using R Markdown document such that it is made interactive using Shiny.

From R studio, click on the `add` icon located on the top left corner:

1. select R Markdown ...
2. From the appeared menue, select 'shiny' from the left panel.
3. Set your document title and author, then press OK.
    
### 1. Create your own document (15 minutes)
In the created interactive document, edit the R chunk named *eruptions* (the second R chunk) to achieve the following:

- Call the **med** data set from the 'BristolVis' library. You can call the data by: 
```{r, eval=FALSE}
data(med, package="BristolVis")
```

- Create an interactive histogram representing either *age* or *time* on its x-axis based on a user input.

- Add a suitable control using the 'sliderInput' for the number of bins of the plotted histogram.

- Add an animation function for the added 'sliderInput' and check its effect.

```{r med-histogram, echo=TRUE, eval=FALSE}
library(BristolVis)
library(shiny)
library(ggplot2)

data(med, package = 'BristolVis')
inputPanel(
  selectInput("HistSelVar", label = "Select variable:",
              choices = c('Age' = 'age', 'Time to effect' = 'time'), selected = 'age'),
  
  sliderInput("SelBin", label = "Number of bins:",
              min = 1, max = 50, value = 6, step = 1, animate = TRUE)
)

renderPlot({
  ggplot2::ggplot(data = med, aes_string(x = input$HistSelVar)) +
    geom_histogram(bins = input$SelBin)
})
```

### 2. Add an interactive scatter plot (15 minutes)

In the same document add another shiny input and output items to create a scatter plot for age Vs. time grouped by the aesthestic colour that is mapped to one of the following categorical variables based on a user input: Gender; General health; treatment.

```{r med-scatter, echo=TRUE, eval=FALSE}
inputPanel(
  selectInput("SelFactor", label = "Select factor",
              choices = c('Gender' = 'gender', 'General Health' = 'health',
                          'Treatment' = 'treatment'), selected = 'gender')
)

renderPlot({
  ggplot(data = med, aes_string(x = 'age', y = 'time')) +
    geom_point(aes_string(colour=input$SelFactor))
})
```

### 3. Embed a shiny application (5 minutes)

It's always possible to embed an entire Shiny application (pre-written) within your R Markdown document using the `shinyAppDir` function. 

- Add a new R chunk to your document to embed the 'hello' Shiny application located in the example directory of the shiny package (use: `r system.file("examples/01_hello", package="shiny")` to locate the directory of the app):

```{r, echo=TRUE, eval=FALSE}
shinyAppDir(
  system.file("examples/01_hello", package="shiny"),
  options=list(
    width="100%", height=550
  )
)
```
