---
title: "Practical - Intro-R"
author: "Osama Mahmoud"
output: rmarkdown::html_vignette
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Practical - Intro-R}
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = FALSE)
```

## Exercise 1:
Data on heights, weights and gender were collected for 10 individuals in early-adulthood. The data were reported in the table below (heights measured in cm, weights in Kg and m refers to a male gender):

```{r, eval=TRUE, echo=FALSE}
DT = data.frame(id = 1:10,
                ht=c(155, 152, 164, 175, 193, 203, 190, 183, 155, 169),
                wt=c(80, 85, 72, 69, 86, 110, 106, 96, 90, 89),
                gender=c("m", "m", "f", "m", "f", "f", "f", "m", "f", "m"))
knitr::kable(DT)
```
  
  a) Create vectors for height, weight and gender and assigned them to the names: `ht`; `wt`; `gender` respectively.
  
```{r}
ht = c(155, 152, 164, 175, 193, 203, 190, 183, 155, 169)
wt = c(80, 85, 72, 69, 86, 110, 106, 96, 90, 89)
gender = c("m", "m", "f", "m", "f", "f", "f", "m", "f", "m")
```

  b) Using `ht` and `wt` vectors, creat a new variable for the BMI (Hint: BMI is calculated by dividing weight measured in Kg by the squared height measured in **meters**)

```{r}
# convert 'ht' into meters
ht_meters = ht / 100
# BMI calculations
(BMI = wt/(ht_meters^2))
```

  c) Show the length of the `ht` vector.
  
```{r}
length(ht)
```

  
  d) Show a frequency table for the `gender` variable (Hint: search the help for the table function by typing in `?table`)

```{r, message=FALSE}
?table
table(gender)
```

  e) Round the calculated BMI values to 2 decimel digits only.
  
```{r}
(BMI = round(BMI, digits = 2))
```

  f) Create a new `data.frame` with the name `DT` that includes height, in meters, weight, in Kg, BMI, and gender.
  
```{r}
(DT = data.frame(ht_meters = ht/100, wt = wt, BMI = BMI, gender = gender))
```

  g) Add a logical variable to the `DT`, with a name of `obese` whose values are `TRUE` for subjects with weights over 95 Kg.

```{r}
(DT$obese = DT$wt > 95)
```

  
  h) Find out how many subjects with weights over 95 Kg.
  
```{r}
sum(DT$wt > 95)
# or alternatively
sum(DT$obese)
```

  i) Extract the BMI for the 3rd and 5th individuals.
  
```{r}
DT$BMI[c(3,5)]
```
