---
title: "Practical - Base graphics"
author: "Osama Mahmoud"
output: rmarkdown::html_vignette
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Practical - Base graphics}
-->

We are going to investigate a brief form of the IMDB (*movies*) data set. Movies
were selected for inclusion if they had a known length, had been rated by at
least one IMDB user and had an mpaa rating. This gives $4847$ films, where each
film has $24$ associated variables. The data can be called and viewed using:

```{r}
data(bmov, package = "BristolVis")
head(bmov)
```

### Scatter plots (20 minutes)

Let's start with some simple scatter plots using the `bmov` data:

1. Plot length Vs. rating.
```{r echo=FALSE, eval=FALSE}
plot(bmov$Length, bmov$Rating)
```
2. Use the `xlab` and `ylab` arguments to specify suitable axis labels.
```{r echo=FALSE, eval=FALSE}
plot(bmov$Length, bmov$Rating, xlab="Length", ylab="Rating")
```
3. Use the `ylim` argument to specify a y-axis range from 1 to 10.
```{r echo=FALSE, eval=FALSE}
plot(bmov$Length, bmov$Rating, xlab="Length", ylab="Rating", ylim = c(1,10))
```
4. Use the `col` argument to change the colour of the points.
```{r echo=FALSE, eval=FALSE}
plot(bmov$Length, bmov$Rating, xlab="Length", ylab="Rating",
     ylim = c(1,10), col = 2)
```
5. Use the `main` argument to give the plot a suitable title.
```{r echo=FALSE, eval=FALSE}
plot(bmov$Length, bmov$Rating, xlab="Length", ylab="Rating",
     ylim = c(1,10), col = 2, main = "Movie rating against length")
```
6. If we altered the default plot parameters using:
```{r}
op = par(mar=c(3,3,2,1), tck=-.01, las=1, cex.axis=0.4)
```
and generated our plot in (5) again, what will happen? can you figure out what *mar*, *tck*, *las* and *cex.axis* do?

7. Reset your plot device using:
```{r}
par(op)
```
and generate the last plot again. Do you see the reset effect?

### Histograms (20 minutes)
We will now investigate the distribution of movie years using histograms.

1. Use the `hist` function to plot a histogram of the movie years.
```{r echo=FALSE, eval=FALSE}
hist(bmov$Year)
```
2. The default method for determining the number of bins isn't great. Use different rules to set breaks to `15`.
```{r echo=FALSE, eval=FALSE}
hist(bmov$Year, breaks = 15)
```
3. Use the `xlab` and `ylab` arguments to specify suitable axis labels.
```{r echo=FALSE, eval=FALSE}
hist(bmov$Year, breaks = 15, xlab = "Year", ylab = "Counts")
```
4. Use the `col` argument to change the colour of the histogram.
```{r echo=FALSE, eval=FALSE}
hist(bmov$Year, breaks = 15, xlab = "Year", ylab = "Counts", col = 3)
```
5. Use the `main` argument to give the plot a suitable title.
```{r echo=FALSE, eval=FALSE}
hist(bmov$Year, breaks = 15, xlab = "Year", ylab = "Counts", col = 3,
     main = "Histogram for years of the movies")
```

### Boxplots (10 minutes)
1. Generate a boxplot for the ratings data.
```{r echo=FALSE, eval=FALSE}
boxplot(bmov$Rating)
```
2. Separate the data by whether the movie is a romantic movie.
```{r echo=FALSE, eval=FALSE}
boxplot(bmov$Rating ~ bmov$Romance)
```
3. Try generating a similar boxplot, but for other variables. What
happens when you condition on more than one variable? e.g. `Romance` and `Action`.
```{r echo=FALSE, eval=FALSE}
boxplot(bmov$Rating ~ bmov$Romance + bmov$Action)
```
